---
title: "analysis1"
author: "Sridhar"
date: "4 February 2018"
output: html_document
---

```{r}
library("ggplot2")
library("corrplot")
```

## Including the dataset

```{r}
train <- read.csv("train.csv",stringsAsFactors = F)
test <- read.csv("test.csv",stringsAsFactors = F)
```

## What the data has

```{r}
head(train)
```
```{r}
str(train)
```
Variable    Name	Description
Survived	  Survived (1) or died (0)
Pclass	    Passenger’s class
Name	      Passenger’s name
Sex	        Passenger’s sex
Age	        Passenger’s age
SibSp	      Number of siblings/spouses aboard
Parch	      Number of parents/children aboard
Ticket	    Ticket number
Fare	      Fare
Cabin	      Cabin
Embarked	  Port of embarkation

## Clean it
```{r}
train <- na.omit(train)
test <- na.omit(test)
```


## Age relations - Sounds insane!

```{r}
cor.test(train$Survived,train$Age)
```
```{r}
num_train <- train[,sapply(train, is.numeric)]
cm <-cor(num_train)
```

```{r}
corrplot(cm,method = "shade")
```

```{r}

```

Survived is correlated with Fare

```{r}

```

